TITLE OF YOUR PROJECT

### 2024-11-04 A3-Pt2.Rmd
Update A3-Pt2.Rmd

---
title: "TITLE OF YOUR PROJECT"
author: "PUT YOUR MYLS GROUP NUMBER HERE, THEN LIST GROUP MEMBERS BELOW"
date: "November 12th, 2024"
output: pdf_document
---

@@

- John K. Samson (#########)
- John Darnielle (#########)
- Craig Finn (#########)
- Joel Plaskett (########)
- Ezra Furman (#########)

>>>>

---
title: "TITLE OF YOUR PROJECT"
author: "Group 8"
date: "November 12th, 2024"
output: pdf_document
---

@@

- Aditya Chauhan (169027493)
- John Darnielle (#########)
- Craig Finn (#########)
- Joel Plaskett (########)
- Ezra Furman (#########)
